### 2023-11-11 manuscript/manuscript.Rmd
fix typo
include data preparation information

The input data consists of a sample by accurate *m/z* feature intensity matrix with at least four samples.
It is recommended that these data are pre-treated prior to assignment.
Pre-treatment steps such as occupancy or QC based RSD filtering can ensure the robustness of the *m/z* that are considered. 
Other steps such as batch correction, imputation and TIC normalisation can improve the strength of *m/z* correlations by removing variability introduced during MS analysis.

>>>>

The input data simply consists of a sample by accurate *m/z* feature intensity matrix with at least four samples.
It is recommended that these data are pre-treated prior to assignment and data preparation can be performed by a software tool of the user's preference.
Pre-treatment steps such as occupancy or QC-based RSD filtering can ensure the robustness of the *m/z* that are considered. 
Other steps such as batch correction, imputation and TIC normalisation can improve the strength of *m/z* correlations by removing variability introduced during MS analysis.
